Age-related changes in plant growth and traits

### 2015-05-07 results_best.Rmd
some script at bottom starting to extract counts of reproductive parts from Konrad's data

>>>>

#Working to get counts out of Konrad's reproduction data
tmpBAER <- BAER_Investment
FD_BAER <- as.data.frame(tmpBAER$FD)
Error_BAER <- as.data.frame(tmpBAER$Error)
View(FD_BAER)

BAER_count <- FD_BAER %>%
  group_by(Individual, what) %>%
  summarise_each(funs(sum), count, weight)

BAER_count2 <- Error_BAER %>%
  group_by(Individual, Element) %>%
  summarise_each(funs(sum), Count)

BAER_count2 <- subset(BAER_count2,Count>0)

names(BAER_count2)=c("Individual","what","Error")
BAER_count <- merge(BAER_count,BAER_count2,by=c("Individual","what"),all=TRUE)
